LCS Tool: A Computational Platform for Lagrangian Coherent Structures

### 2014-10-21 main.tex
Reformat FIXME
Address reviewer comment

% FIXME Reviewer #3, comment #3: The comparison with other publicly available LCS detection software should include more details. It contains a very high-level summary of LCS tool being an "all-purpose numerical engine". That part should be revisited and become more concrete.
Software for LCS detection includes the following packages:
\begin{itemize}
\item \emph{MANGEN}\citep{lekien03:_time} calculates FTLE and advects material curves in two dimensional velocity fields. It also includes a graphical user interface and uses MPI for parallel calculations.
% FIXME Cannot cite LCS MATLAB Kit without a journal reference
% \item \emph{LCS MATLAB Kit}\citep{dabiri09:_lmk} calculates the FTLE from velocity datasets. Includes a graphical user interface.
\item \emph{Newman}\citep{toit10:_trans} calculates the FTLE in $N$ dimensions. Assists ridge extraction of FTLE fields. Supports analytic  and dataset based velocity definitions.
% FIXME Cannot cite FlowVC without a journal reference
% \item \emph{FlowVC}\citep{shadden10:_flowvc} is a general purpose LCS platform for two and three dimensional datasets. Parallel calculations are supported with Open\-MP, CUDA and OpenCL.
% FIXME FlowTK
% https://github.com/FlowPhysics/FlowTK
% doi:10.1007%2F978-3-319-04099-8_13
\end{itemize}
These packages primarily target the automated generation of FTLE plots to aid the visual assessment of hyperbolic LCSs in the flow. The purpose of LCS Tool and this article is to provide an all-purpose numerical engine for the geodesic extraction of LCSs as parametrized material curves in unsteady two-dimensional flows, and extend the scope of such extraction to elliptic LCSs.

@@

% FIXME Reviewer #3, comment #2: "As for a platform, efficiency is also a matter in consideration. Performance degradation is not expected as a cost of generalized computational paradigm. That part should be at least mentioned along with the applications to make the article technically more sound."

@@

In this section we present examples of the use of LCS Tool to obtain LCSs in three different examples: a double gyre, a jet, and an oceanic geostrophic flow. All three examples are available as demonstration files in the demo folder of LCS Tool. By executing these scripts, readers can follow LCS Tool computations step by step.

>>>>

% FIXME Reviewer #3, comment #3: The comparison with other publicly available LCS detection software should include more details. It contains a very high-level summary of LCS tool being an "all-purpose numerical engine". That part should be revisited and become more concrete.
Software for LCS detection includes the following packages:
\begin{itemize}
\item \emph{MANGEN}\citep{lekien03:_time} calculates FTLE and advects material curves in two dimensional velocity fields. It also includes a graphical user interface and uses MPI for parallel calculations.
% FIXME Cannot cite LCS MATLAB Kit without a journal reference
% \item \emph{LCS MATLAB Kit}\citep{dabiri09:_lmk} calculates the FTLE from velocity datasets. Includes a graphical user interface.
\item \emph{Newman}\citep{toit10:_trans} calculates the FTLE in $N$ dimensions. Assists ridge extraction of FTLE fields. Supports analytic  and dataset based velocity definitions.
% FIXME Cannot cite FlowVC without a journal reference
% \item \emph{FlowVC}\citep{shadden10:_flowvc} is a general purpose LCS platform for two and three dimensional datasets. Parallel calculations are supported with Open\-MP, CUDA and OpenCL.
% FIXME Add FlowTK, https://github.com/FlowPhysics/FlowTK, doi:10.1007%2F978-3-319-04099-8_13
\end{itemize}
These packages primarily target the automated generation of FTLE plots to aid the visual assessment of hyperbolic LCSs in the flow. The purpose of LCS Tool and this article is to provide an all-purpose numerical engine for the geodesic extraction of LCSs as parametrized material curves in unsteady two-dimensional flows, and extend the scope of such extraction to elliptic LCSs.

@@

@@

This section presents the use of LCS Tool in three examples: a double gyre, a jet, and an oceanic geostrophic flow. The examples are available as scripts in the demo folder of LCS Tool. Executing these scripts can help readers follow LCS Tool computations.

% FIXME Performance also described in Conclusions section
The scripts call LCS Tool functions.
These functions are written to achieve balance between ease of use and performance.
% FIXME List demo script run-times in minutes in a table
Running the demo scripts takes on the order of minutes.
